Open Policing Project - City: Coverage Rates

### 2018-10-26 lib/bunching_report.Rmd
progress

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(tbl, division, hour_of_day, age_group, vehicle_make)
bt$results$plots$over
bt$results$plots$coefficient
bt$results$plots$bunching
bt$results$plots$lenience
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(tbl, region, hour_of_day, vehicle_type)
bt$results$plots$over
bt$results$plots$coefficient
bt$results$plots$bunching
bt$results$plots$lenience
```
\newpage

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(tbl, hour_of_day, vehicle_make)
bt$results$plots$over
bt$results$plots$coefficient
bt$results$plots$bunching
bt$results$plots$lenience
```

>>>>

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(tbl, division, hour_of_day, age_group, vehicle_make)
bt$results$plots$over
bt$results$plots$bunching
bt$results$plots$lenience
bt$results$plots$coefficient
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(tbl, region, hour_of_day, vehicle_type)
bt$results$plots$over
bt$results$plots$bunching
bt$results$plots$lenience
bt$results$plots$coefficient
```
\newpage

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(tbl, hour_of_day, vehicle_make)
bt$results$plots$over
bt$results$plots$bunching
bt$results$plots$lenience
bt$results$plots$coefficient
```
